Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-22 WSSSPE3/report/wg_main_publishing_SW.tex
adding a crossref and removing a comment
Added label, fixed minor typo

\subsection{Publishing Software Working Group Discussion}

@@

Transitive Credit: Since these forms of publishing must make their sources explicit,
they should be easier to trace even if appropriately worded credit for software
is not provided. In addition, these notebooks make it possible to provide/define
additional metadata to make the tracing of credit clearer. In addition, attributions
could be added to citations to identify whether a paper extends a result, verifies it,
contradicts it, etc.

@@

The afforementioned page to be published on SSI.

>>>>

\subsection{Publishing Software Working Group Discussion} \label{sec:publishing-software}

@@

Software Credit (\S\ref{sec:software-credit}): Since these forms of publishing must make their sources explicit,
they should be easier to trace even if appropriately worded credit for software
is not provided. In addition, these notebooks make it possible to provide/define
additional metadata to make the tracing of credit clearer. In addition, attributions
could be added to citations to identify whether a paper extends a result, verifies it,
contradicts it, etc.

@@

The aforementioned page to be published on SSI.
